\addchap{Preface}
This book covers the material from the Applied Mathematics in Physics and Engineering course at Berea College. 

This textbook is the result of the effort of many people. It is a compendium of the work that appears in the following open source textbooks: Trigonometry from Micheal Corral, and Light and Matter from Benjamin Crowell.

The Introduction and Scaling chapters are due to Benjamin Crowell from Fullerton College. Micheal Corral from Schoolcraft College contributed to the sections on Vectors in Euclidian Space, General Triangle, Radian Measure,
Right triangle, General Triangles, Identities, Graphing and Inverse functions and Additional Topics.  

Following their work, this book is also released under the GNU Free Documentation License, which allows others to not only copy and distribute the book but also to modify it. Permission is granted to copy, distribute and/or modify this document under the terms of the GNU Free Documentation License, Version 1.2 or any later version published by the Free Software Foundation; with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts. A copy of the license is included in the section entitle ``GNU Free Documentation License.''

The original form of this book is LaTeX source code. Compiling this LaTeX source has the effect of generating a device-independent representation of a book, which can be converted to other formats and printed. This book was typeset by the authors using latex, pdflatex, dvips among other free, open-source programs. The graphics were created using MetaPost, TikZ and Gnuplot.

There are numerous exercises throughout the text, which in my experience are more than enough for a semester course in this subject.

Finally, I would like to thank my students in PHY 130 for being the guinea pigs for the initial draft of this book, and for finding the numerous errors and typos it contained.

\begin{flushleft}
\emph{August 2020}\hspace{\stretch{1}}\textsc{Martin Veillette}
\end{flushleft}
